Very simplified likelihood

### 2024-02-22 inst/very_simplified_likelihood.Rmd
edge cases (r=0 -> p=1; r=n -> p=0

```{r,label=defmle}
MLE <- function(r,n,give=FALSE){
    d <- 1e-6
     jj <- optimize(f_vec_arn,c(d,1-d),r=r,n=n,log=TRUE,maximum=TRUE)
	 if(!give){jj <- jj$maximum}
	 return(jj)
}

MLEa <- function(r,n,give=FALSE){
	jj <- uniroot(
		f=function(a){fdash(a,r,n)},
		interval=c(0.01,0.99))
	if(!give){jj <- jj$root}
	return(jj)
}

>>>>

```{r,label=defmle}
MLE <- function(r,n,give=FALSE){
	d <- 1e-6
	if(r==n){
		out <- 0
	} else if(r==0){
		out <- 1
	} else {
		out <- optimize(f_vec_arn,c(d,1-d),r=r,n=n,log=TRUE,maximum=TRUE)
		if(!give){out <- out$maximum}
	}
	return(out)
}

MLEa <- function(r,n,give=FALSE){
	if(r==n){
		out <- 0
	} else if(r==0){
		out <- 1
	} else {
		out <- uniroot(f=function(a){fdash(a,r,n)},interval=c(0.01,0.99))
		if(!give){out <- out$root}
	}
	return(out)
}
